Realizing temporal graphs from fastest travel times

### 2023-02-27 Arxiv-17-2-23/arxiv.tex
arxiv version

%
\begin{figure}[t]
	\noindent
	\makebox[\textwidth]{
		\centering
\begin{tikzpicture}%[xscale=2]

	%%Variable X1
	\node (x1t) at (1,0) {};
	\node (x1f) at (3,0) {};

	%%Variable X2
	\node (x2t) at (5,0) {};
	\node (x2f) at (7,0) {};

	%%Variable x3
	\node (x3t) at (9,0) {};
	\node (x3f) at (11,0) {};

	%%Variable x4
	\node (x4t) at (13,0) {};
	\node (x4f) at (15,0) {};

	%% edges among xt, xf vertices
	%x1 to all
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);

	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
	%x2 to all
	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);

	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
	%x3 to all
	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);

	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);

	%%Variable X1
	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
	\draw (x1t) -- (x1f) -- (x1) -- (x1t);

	%%Variable X2
	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
	\draw (x2t) -- (x2f) -- (x2) -- (x2t);

	%%Variable x3
	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
	\draw (x3t) -- (x3f) -- (x3) -- (x3t);

	%%Variable x4
	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
	\draw (x4t) -- (x4f) -- (x4) -- (x4t);

	%%vertices for clauses c1, c2 + vertex v
	\node[vert,label=above:$v$] (v) at (8,3) {};
	\node[vert,label=below:$c_1$] (c1) at (4.5,-3) {};
	\node[vert,label=below:$c_2$] (c2) at (11.5,-3) {};

	%%% edges between x1 gadget and v,c1,c2
	\draw (x1t) to node[timelabel] {$1$} (c1);
	\draw (x1t) to node[timelabel] {$1$} (c2);
	\draw (x1t) to [out=90,in=190] (v);
	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);

	%%% edges between x2 gadget and v,c1,c2
	\draw (x2f) to node[timelabel] {$1$} (c1);
	\draw (x2t) to node[timelabel] {$1$} (c2);
	\draw (x2t) to [out=80,in=210]  (v);
	\draw (x2f) to node[timelabel] {$3$} (v);

	%%% edges between x3 gadget and v,c1
	\draw (x3t) to node[timelabel] {$1$} (c1);
	\draw (x3t) to node[timelabel] {$3$} (v);
	\draw (x3f) to [out=100,in=330] (v);

	%%% edges between x4 gadget and v,c2
	\draw (x4t) to node[timelabel] {$1$} (c2);
	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
	\draw (x4f) to [out=90,in=360] (v);

\end{tikzpicture}
}
\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
where all unlabeled edges get the label $2$.
}\label{fig:NP-example}
\end{figure}
%
We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
where $u,v$ are two vertices of $G$. 
We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
\begin{itemize}
    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
    %$d(x_1,x_2)=2$. 
    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
    \item For each clause $c$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
    If $x_i$ appears non-negated in $c$ we specify the following durations:
    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
    If $x_i$ appears negated in $c$ we specify the following duratios:
    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
    and
    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
    $d(x_i,x_j)=2\Delta +1$ and
    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
    $d(c_i,c_j)= \Delta + 1$.
\end{itemize}
This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. In the remainder we show that $(D,\Delta)$ is a \textsc{Yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.

@@

\begin{figure}%[t]
\noindent\makebox[\textwidth]{
\centering
%\begin{center}
\begin{tikzpicture}[line width=1pt, scale=.65]
\scriptsize
\node (A) at (14,0) {};

\draw[rounded corners, dashed, gray] (-13, 5) rectangle (10, 1.5) {};
\node (A) at (-10.5,4.5) {alignment gadget};

\draw[rounded corners, dotted, gray] (-14, -2.5) rectangle (-10.5, -9.5) {};
\draw[rounded corners, dotted, gray] (-14, -12.5) rectangle (-10.5, -19.5) {};
\draw[rounded corners, dotted, gray] (7.5, -2.5) rectangle (11, -9.5) {};
\draw[rounded corners, dotted, gray] (7.5, -12.5) rectangle (11, -19.5) {};
\node[rotate=90] (A) at (-14.5,-16) {connector gadget};

\draw[rounded corners, dashed, gray] (-9.5, 1) rectangle (1.5, -26) {};
\node (A) at (-4,-25.5) {edge selection gadget for $i,j$};

\draw[rounded corners, dashed, gray] (3.5, 1) rectangle (6.5, -26) {};
\node[rotate=-90] (A) at (7,-23) {verification gadget for $j$};

    \node[vert,label=above:$w^\star$, fill=gray] (W) at (-2,4) {};
    \node[vert] (W1) at (-6.5,2) {};
    \node[vert] (W2) at (-10,2) {};
    \node[vert] (W3) at (-12,2) {};
    \node[vert] (W4) at (7,2) {}; 
    \node[vert] (W5) at (3.5,2) {};
    \node[vert] (W6) at (9,2) {};

    \node[vert,label=left:$\hat{v}_0$] (VH11) at (-11,-3) {}; 
    \node[vert,label=left:$\hat{v}_0'$] (VH111) at (-13,-3) {}; 
    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH12) at (-12,-5) {}; 
    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH13) at (-12,-7) {}; 
    \node[vert,label=left:$\hat{v}_3$] (VH14) at (-11,-9) {};  
    \node[vert,label=left:$\hat{v}_3'$] (VH144) at (-13,-9) {};

    \node[vert,label=left:$\hat{v}_0$] (VH21) at (-11,-13) {};
    \node[vert,label=left:$\hat{v}_0'$] (VH211) at (-13,-13) {}; 
    \node[vert,label=left:$\hat{v}_1$, fill=gray] (VH22) at (-12,-15) {}; 
    \node[vert,label=left:$\hat{v}_2$, fill=gray] (VH23) at (-12,-17) {};
    \node[vert,label=left:$\hat{v}_3$] (VH24) at (-11,-19) {};
    \node[vert,label=left:$\hat{v}_3'$] (VH244) at (-13,-19) {};

    \node[vert,label=right:$\hat{v}_0$] (VH31) at (8,-3) {}; 
    \node[vert,label=right:$\hat{v}_0'$] (VH311) at (10,-3) {}; 
    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH32) at (9,-5) {}; 
    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH33) at (9,-7) {}; 
    \node[vert,label=right:$\hat{v}_3$] (VH34) at (8,-9) {};  
    \node[vert,label=right:$\hat{v}_3'$] (VH344) at (10,-9) {};

    \node[vert,label=right:$\hat{v}_0$] (VH41) at (8,-13) {}; 
    \node[vert,label=right:$\hat{v}_0'$] (VH411) at (10,-13) {}; 
    \node[vert,label=right:$\hat{v}_1$, fill=gray] (VH42) at (9,-15) {}; 
    \node[vert,label=right:$\hat{v}_2$, fill=gray] (VH43) at (9,-17) {}; 
    \node[vert,label=right:$\hat{v}_3$] (VH44) at (8,-19) {};  
    \node[vert,label=right:$\hat{v}_3'$] (VH444) at (10,-19) {};

    \node[vert,label=above:$x_1$] (X1) at (-8,0) {}; 
    \node[vert,label=above:$x_2$] (X2) at (-6,0) {}; 
    \node[vert,label=above:$x_3$] (X3) at (-4,0) {}; 
    \node (A) at (-2,0) {$\ldots$};
    \node[vert,label=above:$x_m$] (XM) at (0,0) {};

    \node[vert,label=left:$v_{i,j}^\star$, fill=gray] (VS) at (-4,-3) {};

    \node[vert,label=left:$u^1_0$] (Y1) at (-8,-6) {}; 
    \node[vert,label=left:$u^2_0$] (Y2) at (-6,-6) {}; 
    \node[vert,label=left:$u^3_0$] (Y3) at (-4,-6) {}; 
    \node (A) at (-2,-6) {$\ldots$};
    \node[vert,label=right:$u^m_0$] (YM) at (0,-6) {};

    \node[vert,label=left:$u^1_1$] (U11) at (-8,-8) {}; 
    \node[vert,label=left:$u^2_1$] (U12) at (-6,-8) {}; 
    \node[vert,label=left:$u^3_1$] (U13) at (-4,-8) {}; 
    \node (A) at (-2,-8) {$\ldots$};
    \node[vert,label=right:$u^m_1$] (U1M) at (0,-8) {};

    \node[vert,label=left:$u^1_2$] (U21) at (-8,-10) {}; 
    \node[vert,label=left:$u^2_2$] (U22) at (-6,-10) {}; 
    \node[vert,label=left:$u^3_2$] (U23) at (-4,-10) {}; 
    \node (A) at (-2,-10) {$\ldots$};
    \node[vert,label=right:$u^m_2$] (U2M) at (0,-10) {};

    \node (A) at (-8,-11.5) {$\vdots$}; 
    \node (A) at (-6,-11.5) {$\vdots$}; 
    \node (A) at (-4,-11.5) {$\vdots$}; 
    \node (A) at (0,-11.5) {$\vdots$};

    \node[vert,label=left:$u^1_n$] (UN1) at (-8,-13) {}; 
    \node[vert,label=left:$u^2_n$] (UN2) at (-6,-13) {}; 
    \node[vert,label=left:$u^3_n$] (UN3) at (-4,-13) {}; 
    \node (A) at (-2,-13) {$\ldots$};
    \node[vert,label=right:$u^m_n$] (UNM) at (0,-13) {};

    \node[vert,label=left:$u_{n+1}^1$] (UN11) at (-8,-17) {}; 
    \node[vert,label=left:$u_{n+1}^2$] (UN12) at (-6,-17) {}; 
    \node[vert,label=left:$u_{n+1}^3$] (UN13) at (-4,-17) {}; 
    \node (A) at (-2,-17) {$\ldots$};
    \node[vert,label=right:$u_{n+1}^m$] (UN1M) at (0,-17) {};

    \node (A) at (-8,-18.5) {$\vdots$}; 
    \node (A) at (-6,-18.5) {$\vdots$}; 
    \node (A) at (-4,-18.5) {$\vdots$}; 
    \node (A) at (0,-18.5) {$\vdots$};

    \node[vert,label=left:$u_{4n}^1$] (U2N1) at (-8,-20) {}; 
    \node[vert,label=left:$u_{4n}^2$] (U2N2) at (-6,-20) {}; 
    \node[vert,label=left:$u_{4n}^3$] (U2N3) at (-4,-20) {}; 
    \node (A) at (-2,-20) {$\ldots$};
    \node[vert,label=right:$u_{4n}^m$] (U2NM) at (0,-20) {};

    \node[vert,label=left:$v_{i,j}^{\star\star}$, fill=gray] (VSS) at (-4,-24) {};

    \node[vert,label=right:$y^j$] (YI) at (5,0) {};
    \node[vert,label=right:$v_0^j$, fill=gray] (VI0) at (5,-2) {};
    \node[vert,label=right:$v_1^j$, fill=gray] (VI1) at (5,-4) {};
    \node (A) at (5,-5.5) {$\vdots$};
    \node[vert,label=right:$v_{i-1}^j$, fill=gray] (VIJ1) at (5,-7) {};
    \node[vert,label=right:$v_{i}^j$, fill=gray] (VIJ) at (5,-11) {};
    \node (A) at (5,-12.5) {$\vdots$};
    \node[vert,label=right:$v_{j-1}^j$, fill=gray] (VII1) at (5,-14) {};
    \node[vert,label=right:$\hat{u}_{1}^j$] (UI1) at (5,-16) {};
    \node[vert,label=right:$\hat{u}_{2}^j$] (UI2) at (5,-18) {};
    \node (A) at (5,-19.5) {$\vdots$};
    \node[vert,label=right:$v_{j}^j$, fill=gray] (UIN3) at (5,-21) {};
    \node (A) at (5,-22.5) {$\vdots$};
    \node[vert,label=right:$v_{k}^j$, fill=gray] (VIK) at (5,-24) {};

	\draw[edge, line width=1.5pt] (X1) --node[timelabel] {$t_1$} (VS);
	\draw[edge] (X2) --node[timelabel] {$t_2$} (VS);
	\draw[edge] (X3) --node[timelabel] {$t_3$} (VS);
	\draw[edge] (XM) --node[timelabel] {$t_m$} (VS);

    \draw[edge] (Y1) --node[timelabel,sloped] {$t_3+2$} (VS);
	\draw[edge] (Y2) --node[timelabel,sloped] {$t_m+2$} (VS);
	\draw[edge, line width=1.5pt] (Y3) --node[timelabel,sloped] {$t_1+2$} (VS);
	\draw[edge] (YM) --node[timelabel,sloped] {$t_2+2$} (VS);

    \draw[edge] (Y1) --node[timelabel] {$t_3+4$} (U11);
	\draw[edge] (Y2) --node[timelabel] {$t_m+4$} (U12);
	\draw[edge, line width=1.5pt] (Y3) --node[timelabel] {$t_1+4$} (U13);
	\draw[edge] (YM) --node[timelabel] {$t_2+4$} (U1M);

    \draw[edge] (U21) --node[timelabel] {$t_3+6$} (U11);
	\draw[edge] (U22) --node[timelabel] {$t_m+6$} (U12);
	\draw[edge, line width=1.5pt] (U23) --node[timelabel] {$t_1+6$} (U13);
	\draw[edge] (U2M) --node[timelabel] {$t_2+6$} (U1M);

    \draw[edge] (UN1) --node[timelabel,sloped] {$t_3+2n+4$} (UN11);
	\draw[edge] (UN2) --node[timelabel,sloped] {$t_m+2n+4$} (UN12);
	\draw[edge, line width=1.5pt] (UN3) --node[timelabel,sloped] {$t_1+2n+4$} (UN13);
	\draw[edge] (UNM) --node[timelabel,sloped] {$t_2+2n+4$} (UN1M);

    \draw[edge] (U2N1) --node[timelabel,sloped] {$t_3+8n+4$} (VSS);
	\draw[edge] (U2N2) --node[timelabel,sloped] {$t_m+8n+4$} (VSS);
	\draw[edge, line width=1.5pt] (U2N3) --node[timelabel,sloped] {$t_1+8n+4$} (VSS);
	\draw[edge] (U2NM) --node[timelabel,sloped] {$t_2+8n+4$} (VSS);

    \draw[edge] (VH11) --node[timelabel,sloped] {$n^9$} (VH12);
	\draw[edge] (VH12) --node[timelabel,sloped] {$n^9+2$} (VH111);
	\draw[edge] (VH12) --node[timelabel] {$n^9+1$} (VH13);
    \draw[edge] (VH13) --node[timelabel,sloped] {$n^9$} (VH14);
	\draw[edge] (VH13) --node[timelabel,sloped] {$n^9+2$} (VH144);

    \draw[edge] (VH21) --node[timelabel,sloped] {$n^9$} (VH22);
	\draw[edge] (VH22) --node[timelabel,sloped] {$n^9+2$} (VH211);
	\draw[edge] (VH22) --node[timelabel] {$n^9+1$} (VH23);
    \draw[edge] (VH23) --node[timelabel,sloped] {$n^9$} (VH24);
	\draw[edge] (VH23) --node[timelabel,sloped] {$n^9+2$} (VH244);

    \draw[edge] (VH31) --node[timelabel,sloped] {$n^9$} (VH32);
	\draw[edge] (VH32) --node[timelabel,sloped] {$n^9+2$} (VH311);
	\draw[edge] (VH32) --node[timelabel] {$n^9+1$} (VH33);
    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9$} (VH34);	
    \draw[edge] (VH33) --node[timelabel,sloped] {$n^9+2$} (VH344);

    \draw[edge] (VH41) --node[timelabel,sloped] {$n^9$} (VH42);
	\draw[edge] (VH42) --node[timelabel,sloped] {$n^9+2$} (VH411);
	\draw[edge] (VH42) --node[timelabel] {$n^9+1$} (VH43);
    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9$} (VH44);	
    \draw[edge] (VH43) --node[timelabel,sloped] {$n^9+2$} (VH444);

	%\draw[edge] (VIJ1) --node[timelabel, near start] {$t_1+4$} (U13);
	%\draw[edge] (VIJ) --node[timelabel, near start] {$t_1+8$} (U23);

    \draw[edge,double] (VIJ1) --node {} (U13);
	\draw[edge,double] (VIJ) --node {} (U23);

	\draw[edge] (W) --node[timelabel] {$1$} (W1);
	\draw[edge] (W) --node[timelabel] {$1$} (W2);
	\draw[edge] (W) --node[timelabel] {$1$} (W3);
	\draw[edge] (W) --node[timelabel] {$1$} (W4);
	\draw[edge] (W) --node[timelabel] {$1$} (W5);
	\draw[edge] (W) --node[timelabel] {$1$} (W6);

	\draw[edge] (X1) --node[timelabel] {$t_1$} (W1);
	\draw[edge] (VH11) --node[timelabel] {$n^9$} (W2);
	\draw[edge] (VH21) edge[bend left=50] node[timelabel] {$n^9$} (W3);
	\draw[edge] (VH31) --node[timelabel] {$n^9$} (W4);
	\draw[edge] (YI) --node[timelabel] {$n^8-1$} (W5);
	\draw[edge] (VH41) edge[bend right=50] node[timelabel] {$n^9$} (W6);

	\draw[edge] (YI) --node[timelabel] {$n^8$} (VI0);

	\draw[edge] (VII1) --node[timelabel] {$t'$} (UI1);
	\draw[edge] (UI1) --node[timelabel] {$t'+2$} (UI2);
\end{tikzpicture}
    %\end{center}
    }
    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
    }\label{fig:hardness1}
\end{figure}

@@

\begin{figure}[t]
%\noindent\makebox[\textwidth]{
\centering
%\begin{center}
\begin{tikzpicture}[line width=1pt, scale=.65]
\scriptsize

\draw[rounded corners, dashed] (-3, -4) rectangle (7, -8) {};
\node (A) at (2,-7) {$V$};

    \node[vert,label=above:$z_1$] (Z1) at (0,0) {};
    \node[vert,label=left:$z_2$, fill=gray] (Z2) at (0,-3) {};
    \node[vert,label=right:$z_3$, fill=gray] (Z3) at (4,-3) {};
    \node[vert,label=above:$z_4$] (Z4) at (4,0) {};

    \node[vert,label=below:$v$] (V) at (-2,-7) {};
    \node[vert,label=below:$v'$] (VV) at (6,-7) {};

    \draw[edge] (Z1) --node[timelabel] {$t$} (Z2);
    \draw[edge] (Z2) --node[timelabel] {$t+2$} (Z3);
    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}-1$} (Z4);

    \draw[edge] (Z2) --node[timelabel] {$t+1$} (V);
    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (V);
    \draw[edge] (Z2) --node[timelabel] {$t+1$} (VV);
    \draw[edge] (Z3) --node[timelabel] {$t+n^{10}$} (VV);
\end{tikzpicture}
    %\end{center}
%    }
    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
\end{figure}

@@

	\begin{figure}[t]
    \centering
	\begin{tikzpicture}[xscale=2]
	%%%S_uv
	\node[vert,label=below:$u$] (v1) at (1,0) {};
	\node[vert] (v2) at (2,0) {};
	\node[vert,label=below:$w$] (v3) at (3,0) {};
	\node[vert] (v4) at (4,0) {};
	\node[vert,label=below:$v$] (v5) at (5,0) {};
	\draw (v1) -- node[timelabel] {$1$} (v2) -- node[timelabel] {$3$}  (v3) -- node[timelabel] {$5$} (v4) -- node[timelabel] {$7$} (v5);
	\draw (v1) to [out=80,in=100,distance=2cm] node[timelabel] {$9$} (v3);

	\draw[transform canvas={yshift=-1.5mm}, blue]
	(v1) edge[diredge2]  node[pos=0.3,yshift=-2,label=below:$P_{u,v}$] {} (v5) ;

	\draw[red]
	(v1) edge[diredge2] [out=85,in=95,distance=2.1cm] node[pos=0.3,yshift=2,label=above:$P_{u,w}$] {} (v3) ;
\end{tikzpicture}
	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
		\label{fig:ftpExample}}
	\end{figure}

@@

    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
    We repeat this for all vertices of interest, and all segments,
    which produces $O(k^{k^2})$ new guesses.
    %
    For an example see~\cref{fig:FPT-guessG7}.
    % counter for guesses continues
    \setcounter{guesscounter}{\value{enumi}}
\end{enumerate}
%
\begin{figure}[t]
    \centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{\linewidth}{!}{
		\begin{tikzpicture}
			%%%S_uv
			\node[vert,label=above:$u {=} v_1$] (v1) at (1,0) {};
			\node[vert,label=above:$v_2$] (v2) at (2,0) {};
			\node[vert,label=above:$v_{p-1}$] (vp1) at (6,0) {};
			\node[vert,label=above:$v_p {=} v$] (vp) at (7,0) {};
			\draw (v1) -- (v2) -- (vp1) -- (vp);

			%%%% S_wz
			\node[vert,label=below:$w {=} z_1$] (z1) at (1,-3) {};
			\node[vert,label=below:$z_2$] (z2) at (2,-3) {};
			\node[vert,label=below:$z_{r-1}$] (zr1) at (6,-3) {};
			\node[vert,label=below:$z_r {=} z$] (zr) at (7,-3) {};
			\draw (z1) -- (z2) -- (zr1) -- (zr);

			\draw [violet] (v2) edge[diredge2] (v1);

			\draw [blue]%[transform canvas={yshift=0.5mm},thick] 
			(v1) edge[dirwave] [out=250,in=120] (z1) 
			(z1) edge[diredge2] (z2);

>>>>

%
\begin{figure}[t]
	\noindent
	\makebox[\textwidth]{
		\centering
	\includegraphics{fig-NP-reduction}
}
\caption{Illustration of the temporal graph $(G,\lambda)$ from the NP-hardness reduction, 
	where the NAE 3-SAT formula $\phi$ is of form $\phi = \text{NAE}(x_1, \overline{x}_2, x_3) \wedge \text{NAE}(\overline{x}_1, x_2, x_4)$.
To improve the readability, we draw edges between vertices $x_i^T$ and $x_j^F$ (where $i \neq j$) with gray dotted lines.
Presented is the labeling of $G$ corresponding to the assignment $x_1=x_2=\textsc{true}$ and $x_3,x_4=\textsc{false}$,
where all unlabeled edges get the label $2$.
}\label{fig:NP-example}
\end{figure}
%
We set $\Delta$ to some constant larger than two, that is, $\Delta\ge 3$. Next, we specify the durations in the matrix $D$ between all vertex pairs.
For the sake of simplicity we write $D_{u,v}$ as $d(u,v)$,
where $u,v$ are two vertices of $G$. 
We start by setting the value of $d(u,v) = 1$ where $u$ and $v$ are two adjacent vertices in $G$.
\begin{itemize}
    %\item For each variable $x$ in $\phi$ we specify the following distances between the non-adjacent variable vertices:
    %$d(x_1,x_2)=2$. 
    %\item For pair of variable $x,y$ in $\phi$ with $x\neq y$ we specify the following 
    %$d(x_1,y^T)=d(x_1,y^F)=3$, $d(x_2,y^T)=d(x_2,y^F)=2$.
    \item For each variable $x_i$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(x_i,v)=2$ and $d(v,x_i)= \Delta $. %, $d(x_2,v)=3$.
    \item For each clause $c$ in $\phi$ and the super vertex $v$
    we specify the following durations:
    $d(c,v)=2$ and $d(v,c)= \Delta - 1$.
    \item Let $x_i$ be a variable that appears in clause $c$, then  we specify the following durations:
    $d(c,x_i)=2$ and $d(x_i,c)=\Delta$.
    If $x_i$ appears non-negated in $c$ we specify the following durations:
    $d(c,x_i^F)=2$ and $d(x_i^F,c)=\Delta$.
    If $x_i$ appears negated in $c$ we specify the following duratios:
    $d(c,x_i^T)=2$ and $d(x_i^T,c)=\Delta$.
    \item Let $x_i$ be a variable that does \emph{not} appear in clause $c$, then we specify the following duratios:
    $d(x_i,c)=\Delta$, $d(c,x_i)=2\Delta + 2$
    and
    $d(c,x_i^T)=d(c,x_i^F)=2$, $d(x_i^T,c)=d(x_i^F,c)=\Delta$. 
    \item For each pair of variables $x_i \neq x_j$ in $\phi$ we specify the following duratios:
    $d(x_i,x_j)=2\Delta +1$ and
    $d(x_i,x_j^T)=d(x_i,x_j^F)=\Delta + 1$.
    \item For each pair of clauses $c_i \neq c_j$ in $\phi$ we specify the following duratios:
    $d(c_i,c_j)= \Delta + 1$.
\end{itemize}
This finishes the construction of the instance $(D,\Delta)$ of \deltaExact\, which can clearly be done in polynomial time. In the remainder we show that $(D,\Delta)$ is a \textsc{Yes}-instance of \deltaExact\ if and only if NAE 3-SAT formula $\phi$ is satisfiable.

@@

\begin{figure}%[t]
\noindent\makebox[\textwidth]{
\centering
\includegraphics{fig-W1-reduction}
    }
    \caption{Illustration of part of the underlying graph $G$ and a possible labeling. Edges incident with vertices of connector gadgets are omitted. Gray vertices form a feedback vertex set.
    The double line connections, between a vertex $v_{i-1}^j$ in the verification gadget, and $u_1^3$ in the edge selection gadget, 
    and, between a vertex $u_2^3$ in the edge selection gadget, and $v_{i}^j$ in the verification gadget,
    consist of $5n$ vertices $a_1^{j,i,3},a_2^{j,i,3},\dots,a_{5n}^{j,i,3}$ 
    and $b_1^{j,i,3},b_2^{j,i,3},\dots,b_{5n}^{j,i,3}$, respectively.
    }\label{fig:hardness1}
\end{figure}

@@

\begin{figure}[t]
%\noindent\makebox[\textwidth]{
\centering

\includegraphics{fig-W1-infinity}
    \caption{Illustration of the infinity gadget. Gray vertices need to be added to the feedback vertex set.}\label{fig:hardness2}
\end{figure}

@@

	\begin{figure}[t]
    \centering
	\includegraphics{fig-motivationExample}
	\caption{An example of a temporal graph, where the fastest temporal path $P_{u,v}$ (in blue) from $u$ to $v$ is of duration $7$,
		while the fastest temporal path $P_{u,w}$ (in red) from $u$ to a vertex $w$, that is on a path $P_{u,v}$, is of duration $1$ and is not a subpath of $P_{u,v}$.		
		\label{fig:ftpExample}}
	\end{figure}

@@

    All together we make two guesses for each pair of vertex $w \in U$ and segment $S_{u,v}$.
    We repeat this for all vertices of interest, and all segments,
    which produces $O(k^{k^2})$ new guesses.
    %
    For an example see~\cref{fig:FPT-guessG7}.
    % counter for guesses continues
    \setcounter{guesscounter}{\value{enumi}}
\end{enumerate}
%
\begin{figure}[t]
    \centering
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{\linewidth}{!}{
		\includegraphics{fig-guess1}}
	\caption{Example of a guess G-\ref{FPT-guessFTPamongv2z2}, where we guessed the fastest temporal paths of form $v_2 \rightarrow u \leadsto w \rightarrow z_2$ (in blue)
	and $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$ (in red).
	\label{fig:FPT-guessG4}}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.48\textwidth}
		\centering
		\resizebox{\linewidth}{!}{

			\includegraphics{fig-guess2}}
		\caption{Example of a guess G-\ref{FPT:guess-uToSegmentz2}, where we guessed the fastest temporal paths of form $w \leadsto u \rightarrow v_2$ (in blue) and $w \leadsto v \rightarrow v_{p-1}$ (in red). 
			\label{fig:FPT-guessG5}}
	\end{subfigure}
